Output Summary

### 2021-12-17 03-post-process/output-plots.Rmd
Update output plots for new model

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny_obs

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pb_Pa_diags
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

```{r make-mean-zero-resid-table}
# extract posterior mean residual time series for each population
resids = lapply(1:4, get_resids, post = post)

>>>>

# which years are "observable" for at least some quantities?
observable = 2:jags_data$ny_obs

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pb_Pa_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

```{r make-mean-zero-resid-table}
# extract posterior mean residual time series for each population
resids = lapply(1:4, get_resids, post = diag_post)
